Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-02-28 paper/paper.tex
done with section 5.1 (for now)

\vspace{1ex}
\subsubsection{Benign traffic.}~Public data sets of bening traffic
exist; they are important to evaluate the rate of false positives of
security tools. We used two popular public sources. The Bigflows.pcap
data set is part of the TcpReplay~\cite{tcpreplay} open source
project. It includes real network traffic of a busy private network
access point to the Internet. We also used the

\Fix{---------------- estou aqui}

In addition to the Bigflows.pcap data
set, we also used data sets\Mar{more than one?}  made available by
Stratosphere Lab~\cite{stratosphere-normal}\Mar{is there a description
  of the traffic? as the description for
  Bigflows.pcap?}. \Luc{@Guilherme ...} \Gui{The Stratosphere IPS Project has a sister project called the Malware Capture Facility Project that is responsible for making the long-term captures. This project is continually obtaining malware and normal data to feed the Stratosphere IPS (copy paste do site). No site tem uma lista de datasets, e embaixo dele descricao da origem desses datasets, como de uma rede universitaria, um usuario normal, etc. https://www.stratosphereips.org/datasets-normal}

\subsubsection{Ground Truth.}To evaluate \tname\ objectively we need
to compare the rules it generates with \emph{trusted rules}. We used
the ``Emerging Threats Open Ruleset''~\cite{emerging-threats-open} for
that. After finding the attack and corresponding rule using the
procedure described in Section~\ref{subsec:malicious-traffic}, we
reproduced the attack and confirmed that the rule captures the
attack. Column ``Ground Truth'' from Table~\ref{table:attacks} only
shows the essential relevant options. Documentation options (\eg{},
``msg'') are discared.

>>>>

\vspace{1ex}
\subsubsection{Benign traffic.}~Public data sets of bening traffic
exist and can be used to evaluate the rate of false positives of
security tools. We used two popular public sources. The Bigflows.pcap
data set is part of the TcpReplay~\cite{tcpreplay} open source
project. It includes real network traffic of a busy private network
access point to the Internet. We also used data sets from the
Stratosphere IPS Project~\cite{stratosphere-normal} including, for
example, the regular traffic of a university network.

%% In addition to the Bigflows.pcap data
%% set, we also used data sets\Mar{more than one?}  made available by
%% Stratosphere Lab~\cite{stratosphere-normal}\Mar{is there a description
%%   of the traffic? as the description for
%%   Bigflows.pcap?}. \Luc{@Guilherme ...} \Gui{The Stratosphere IPS Project has a sister project called the Malware Capture Facility Project that is responsible for making the long-term captures. This project is continually obtaining malware and normal data to feed the Stratosphere IPS (copy paste do site). No site tem uma lista de datasets, e embaixo dele descricao da origem desses datasets, como de uma rede universitaria, um usuario normal, etc. https://www.stratosphereips.org/datasets-normal}

\subsubsection{Ground Truth.}To evaluate \tname\ objectively we need
to compare the rules it generates with \emph{trusted rules}. We used
the ``Emerging Threats Open Ruleset''~\cite{emerging-threats-open} for
that. After finding a matching pair of attack and corresponding rule
using the procedure described in
Section~\ref{subsec:malicious-traffic}, we reproduced the attack to
confirm the rule captures the attack in isolation (and no noise was
introduced in the process). Column ``Ground Truth'' from
Table~\ref{table:attacks} only shows the essential
options. Documentation options (\eg{}, ``msg'') are discared.
